Measuring the double-drift illusion with hand tracking

### 2021-11-20 Manuscript.Rmd
fixed reference

All raw trajectories are show in Figure 2A. In Figure 2C, we plot the average instantaneous heading during the middle second of each 2 _s_ pass for each of the 5 internal motion speeds. The average angle of the tracked path is given in degrees deviation from straight forward. It seems that continuous tracking is sensitive to the strength of the illusion, and this is confirmed by a repeated-measures ANOVA on the average angles, using internal motion as a within-subjects factor ( _F_(4,12)=102.6, _p_<.001, $\eta^2$=0.97 ). With 4 FDR-corrected [@benjamini1995], paired t-tests, we find a difference in heading between internal motion speeds of 0 _cps_ and both 1 _cps_ ( _p_=.022) and -1 _cps_ ( _p_=.025) as well as between -3 and -1 _cps_ and 3 and 1 _cps_ (both _p_ <.001). This makes it clear that continuous tracking does not prevent the illusion from occurring. We will use the heading angle as a measure of the strength of the illusion.

@@

```{r fig5, echo=FALSE, message=FALSE, fig.width=7.5, fig.height=4, fig.cap="\\label{fig:fig5}**Figure 5:** Illusion strength and reset models. **Left:** Illusion strength as in Figure 2 (bottom right); plotted against predicted strength from Eq.1: the arctangent of the ratio of internal to external velocities. Purple dots are the group means from 3 s passes, orange from 4 s passes (2, 3 and 4 _cps_ internal speeds). Predictions from the vector combination model in Eq. 1: black line; $K=0.74$ as in Heller et al. (2021), light blue line; best fit here at $K=0.51$ and the shaded area shows a 95% confidence interval. **Right:** Model limits shown here come from a weighted bootstrapping across participants, lines are median parameter values, shaded areas the 95% confidence intervals of the limits. Gray dots are the reset points from all participants. While a spatial limit provides the better fit, neither a spatial nor a temporal limit explains the data well."}
#plotResetPoints()
#plotModels()
#plotBootstrappedFits()
plotIllusionStrength()
```

>>>>

All raw trajectories are show in Figure 2A. In Figure 2C, we plot the average instantaneous heading during the middle second of each 2 _s_ pass for each of the 5 internal motion speeds. The average angle of the tracked path is given in degrees deviation from straight forward. It seems that continuous tracking is sensitive to the strength of the illusion, and this is confirmed by a repeated-measures ANOVA on the average angles, using internal motion as a within-subjects factor ( _F_(4,12)=102.6, _p_<.001, $\eta^2$=0.97 ). With 4 FDR-corrected [@Benjamini1995], paired t-tests, we find a difference in heading between internal motion speeds of 0 _cps_ and both 1 _cps_ ( _p_=.022) and -1 _cps_ ( _p_=.025) as well as between -3 and -1 _cps_ and 3 and 1 _cps_ (both _p_ <.001). This makes it clear that continuous tracking does not prevent the illusion from occurring. We will use the heading angle as a measure of the strength of the illusion.

@@

```{r fig5, echo=FALSE, message=FALSE, fig.width=7.5, fig.height=4, fig.cap="\\label{fig:fig5}**Figure 5:** Illusion strength and reset models. **Left:** Illusion strength as in Figure 2 (bottom right); plotted against predicted strength from Eq.1: the arctangent of the ratio of internal to external velocities. Purple dots are the group means from 3 s passes, orange from 4 s passes (2, 3 and 4 _cps_ internal speeds). Predictions from the vector combination model in Eq. 1: black line; $K=0.74$ as in Heller et al. (2021), light blue line; best fit here at $K=0.51$ and the shaded area shows a 95% confidence interval. **Right:** Model limits shown here come from a weighted bootstrapping across participants, lines are median parameter values, shaded areas the 95% confidence intervals of the limits. Gray dots are the reset points from all participants. While a spatial limit provides the better fit, neither a spatial nor a temporal limit explains the data well."}
#plotResetPoints()
plotModels()
#plotBootstrappedFits()
#plotIllusionStrength()
```
